\chapter*{Abstract} 
\addcontentsline{toc}{chapter}{Abstract}
\pagestyle{plain}

\paragraph{Introduction} This part of the abstract provides a brief overview of the topic and sets the context for the research. For example: ``This thesis explores the relationship between sleep patterns and academic performance in college students. Understanding this relationship is crucial as it can influence strategies to improve student success.'' 

\paragraph{Research Question} Here, you state the main question your research aims to answer. For instance: The primary research question is: ``How do different sleep patterns affect the academic performance of college students?''

\paragraph{Method} This part explains the approach taken to investigate the research question. For example: ``A survey was conducted with 200 college students to gather data on their sleep habits and academic performance. Additionally, interviews were held with 20 students to obtain more detailed information.''

\paragraph{Results} Summarize the main results of your research and give a brief answer to your research question. For example: ``The results indicate that students with regular sleep schedules tend to have higher GPAs compared to those with irregular sleep patterns. Interviews highlighted that poor sleep often leads to reduced concentration and increased stress.''

\paragraph{Discussion} Discuss the implications of your findings as well as the limitations of your study and suggest future research or practical applications. For example: ``These findings suggest that promoting healthy sleep habits could enhance academic performance. Universities might consider programs to educate students on the importance of sleep. Further research could explore intervention strategies to help students improve their sleep patterns.''